\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students

### 2023-09-18 demystify.tex
update

\begin{enumerate}
    \item \textbf{Cheating}: Cheating, e.g., exams, coding, is a big no-no in the US.  If you're caught cheating, you will face very heavy consequence and likely be expelled from the university (e.g., after the second time at GMU).   This is very different from many international countries where cheating is common and often tolerated.  Faculty is extremely good at detecting cheating (how can we not? we deal with these situations so many times over so many years), and \emph{will} report cheating cases.  In short, whatever you do, don't cheat---not worth it.

>>>>

\begin{enumerate}
    \item \textbf{Cheating}: Cheating, e.g., exams, coding, is a big no-no in the US.  If you're caught cheating, you will face very heavy consequence and likely be expelled from the university (e.g., after the second time at GMU).   This is very different from many international countries where cheating is common and often tolerated.  Faculty is extremely good at detecting cheating (we have been dealing with these situations so many times over so many years), and \emph{will} report cheating cases.  In short, whatever you do, don't cheat---not worth it.
